INSTRUCTIONS TO PREPARE A FULL PAPER FOR THE 9th EUROPEAN CONGRESS ON COMPUTATIONAL METHODS IN APPLIED SCIENCES AND ENGINEERING\break ECCOMAS CONGRESS 2024

### 2024-03-06 paper/paper.tex
paper: fix figure path and labels

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../work/beam/fig_loc_svals_left.pdf}
  \caption{A really Awesome Image}\label{fig:awesome_image1}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../work/beam/fig_loc_svals_inner.pdf}
  \caption{A really Awesome Image}\label{fig:awesome_image2}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{../work/beam/fig_loc_svals_right.pdf}
  \caption{A really Awesome Image}\label{fig:awesome_image3}
\endminipage
\end{figure}

@@

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../work/beam/fig_proj_error_left.pdf}
  \caption{A really Awesome Image}\label{fig:awesome_image1}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../work/beam/fig_proj_error_inner.pdf}
  \caption{A really Awesome Image}\label{fig:awesome_image2}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{../work/beam/fig_proj_error_right.pdf}
  \caption{A really Awesome Image}\label{fig:awesome_image3}
\endminipage
\end{figure}

@@

\begin{figure}[!htb]
    \includegraphics[width=\linewidth]{../work/beam/fig_loc_rom_error.pdf}
    \caption{A really Awesome Image}\label{fig:loc_rom_error}
\end{figure}

>>>>

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_loc_svals_left.pdf}
  \caption{A really Awesome Image}\label{fig:loc_svals_left}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_loc_svals_inner.pdf}
  \caption{A really Awesome Image}\label{fig:loc_svals_inner}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{../figures/beam/fig_loc_svals_right.pdf}
  \caption{A really Awesome Image}\label{fig:loc_svals_right}
\endminipage
\end{figure}

@@

\begin{figure}[!htb]
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_left.pdf}
  \caption{A really Awesome Image}\label{fig:proj_error_left}
\endminipage\hfill
\minipage{0.32\textwidth}
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_inner.pdf}
  \caption{A really Awesome Image}\label{fig:proj_error_inner}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{../figures/beam/fig_proj_error_right.pdf}
  \caption{A really Awesome Image}\label{fig:proj_error_right}
\endminipage
\end{figure}

@@

\begin{figure}[!htb]
    \includegraphics[width=\linewidth]{../figures/beam/fig_loc_rom_error.pdf}
    \caption{A really Awesome Image}\label{fig:loc_rom_error}
\end{figure}
